Staged Abstract Interpreters

### 2019-04-06 paper/90_conc.tex
Grammar conclusion

In this paper, we first present the implementaion of first Futamura projection
on abstract interpreters. To realize it, we design a generic interpreter that
abstracts over both binding-time and value domains; by instantiating it
differently, the staged abstract interpreter can be readily derived.
The meta-programming approach brings new insight and implementation techniques
to optimize abstract interpretation based static analysis. The optimization can
be realized in a compeltely orthogonal way to the abstract semantics and actual
implementation code. We empirical evaluate the performance improved by our approach.

>>>>

In this paper, we first present the implementation of first Futamura projection
on abstract interpreters. To realize it, we design a generic interpreter that
abstracts over both binding-time and value domains; by instantiating it
differently, the staged abstract interpreter can be readily derived.
The meta-programming approach brings new insight and implementation techniques
to optimize abstract interpretation based static analysis. The optimization can
be realized in a completely orthogonal way to the abstract semantics and actual
implementation code. We empirical evaluate the performance improved by our approach.
